Vaccines: Many Beliefs Study 2: jobtalk

### 2019-02-12 study2/job-talk-s2.Rmd
post job talks, pre-reorganization

source("../study1/vacc_import_data.R", chdir = TRUE)
```

@@

@@

ggsave(plot = legend, filename = "../local/legend.png")
```

@@

(
g_diffs <- ggplot(d_diffs,
                  aes(x = reorder(scale, -Mean), y = Mean, 
                      color = condition, group = condition)) +
  # facet_wrap(~ scale, ncol = 3) +
  geom_hline(yintercept = 0, lty = 2, size = 0.5) +
  geom_linerange(aes(ymin = Lower95, ymax = Upper95), position = position_dodge(.25)) +
  geom_linerange(aes(ymin = LowerSD, ymax = UpperSD), 
                 position = position_dodge(.25), size=1.5) +
  geom_point(size = 3, position = position_dodge(.25)) +
  # scale_y_continuous("mean diff") + #, 
                     # limits = c(-3, 3), 
                     # breaks = seq(-3, 3, 1)) +
  # scale_color_brewer(palette = "Set1", direction = -1) +
  scale_color_manual(values=ibm_palette[c(1,3)]) +
  theme_bw(base_size=14) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size=8),
    panel.grid = element_blank()
        ) +
  labs(
    # title = "mean difference scores by scale and condition",
       # subtitle = "error bars are 95% bootstrapped CIs",
       x = "Belief",
       y = "Mean Change Score",
       color = "Condition") 
)

@@

ggsave(plot = vacc_intent_change_plot, filename = "../local/s2_vacc_intent.png", height=4, width=5)
```

>>>>

source("../study1/vacc_import_data.R", chdir = TRUE)

ibm_palette <- c("#648fff", "#785ef0", "#dc267f", "#fe6100", "#ffb000")
```

@@

# ggsave(plot = plt.valid, filename = "../local/s1_predobs_plot.png", width=8.5, height=4)
```

@@

# ggsave(plot = legend, filename = "../local/legend.png")
```

@@

(
g_diffs <- ggplot(d_diffs,
                  aes(x = reorder(scale, -Mean), y = Mean, 
                      color = condition, group = condition)) +
  # facet_wrap(~ scale, ncol = 3) +
  geom_hline(yintercept = 0, lty = 2, size = 0.5) +
  geom_linerange(aes(ymin = Lower95, ymax = Upper95), position = position_dodge(.25)) +
  geom_linerange(aes(ymin = LowerSD, ymax = UpperSD), 
                 position = position_dodge(.25), size=1.5) +
  geom_point(size = 3, position = position_dodge(.25)) +
  # scale_y_continuous("mean diff") + #, 
                     # limits = c(-3, 3), 
                     # breaks = seq(-3, 3, 1)) +
  # scale_color_brewer(palette = "Set1", direction = -1) +
  scale_color_manual(values=ibm_palette[c(3,1)]) + # this is a hack to make it match other fig
  theme_bw(base_size=14) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size=8),
    panel.grid = element_blank()
        ) +
  labs(
    # title = "mean difference scores by scale and condition",
       # subtitle = "error bars are 95% bootstrapped CIs",
       x = "Belief",
       y = "Mean Change Score",
       color = "Condition") 
)

@@

# ggsave(plot = vacc_intent_change_plot, filename = "../local/s2_vacc_intent.png", height=4, width=5)
```
